---
title: "remlTemplate"
author: "SRE"
date: Sys.Date()
output: html_document
editor_options:
  chunk_output_type: console
---

## libraries

```{r libraries}
library(EML)
library(tidyverse)
library(tools)
library(aws.s3)
library(capeml)
library(gioseml)
```

# README

see project README for extracting data from Access database.


## project details

see config.yaml


## algae

```{r algae, eval=TRUE, error=TRUE}

algae <- read_csv("data/Conductivity.csv") %>%
  rename(cluster = `cluster name`) %>%
  mutate(
    `site number` = as.factor(`site number`),
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site acronym` = as.factor(`site acronym`),
    `sample type` = as.factor(`sample type`),
    date = format(as.POSIXct(date, format = "%m/%d/%y %H:%M:%S"), "%Y-%m-%d"),
    date = as.Date(date)
  ) %>%
  select(-ID, -month) %>%
  arrange(date, `site number`) %>%
  filter(!is.na(date))

# write_attributes(algae)
# write_factors(algae)

algae_desc <- "algal characteristics (chlorophyll concentration, cell counts) and specific conductance in canals and reservoirs"

algae_DT <- create_dataTable(
  dfname = algae,
  description = algae_desc)

```


## algal_byproducts

```{r algal_byproducts, eval=TRUE}

algal_byproducts <- read_csv("data/mib and geosmin.csv") %>%
  rename(
    `cluster` = `cluster name`,
    `geosmin (ng/L) ASU`= `Geosmin  (ng/L) ASU`,
    `beta-cyclocitral (ng/L)` = `Beta-cyclocitral (ng/L)`,
    `IPMP recovery (%)` = `IPMP Recovery (%)`,
    `geosmin (ng/L) Phoenix` = `Geosmin  (ng/L) Phoenix`
    ) %>%
mutate(
  cluster = tolower(cluster),
  cluster = as.factor(cluster),
  `site number` = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date = as.Date(date)
  ) %>%
select(-`ID`, -`month`) %>%
arrange(date, `site number`) %>%
filter(!is.na(date))

# write_attributes(algal_byproducts)
# write_factors(algal_byproducts)

algal_byproducts_desc <- "concentration of algal by-products in canals and reservoirs"

algal_byproducts_DT <- create_dataTable(
  dfname = algal_byproducts,
  description = algal_byproducts_desc)

```

## arsenic

```{r arsenic, eval=TRUE}

# complicated import and mutate actions to accomodate text (<2.0) in the
# arsenic concentration column

arsenic <- read_csv(
  file = "data/Arsenic.csv",
  col_types = list(
    col_double(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_double()
  )
  ) %>%
rename(
  `cluster` = `Cluster`,
  `site number` = `Site Number`,
  `site location` = `Site location`,
  `site acronym` = `Site Acronym`,
  `arsenic (ug/L)` = `Arsenic (ug/L)`,
  `perchlorate (ug/L)` = `Perchlorate (ug/L)`
  ) %>%
mutate(
  cluster = tolower(cluster),
  cluster = as.factor(cluster),
  `site number` = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date = format(as.POSIXct(`month/date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date = as.Date(date)
  ) %>%
mutate(
  BDL = case_when(
    grepl("<2.0", `arsenic (ug/L)`, ignore.case = T) ~ 1
  )
  ) %>% # close mutate BDL
mutate(
  `arsenic (ug/L)` = as.numeric(`arsenic (ug/L)`),
  BDL = case_when(
    `arsenic (ug/L)` < 2 ~ 1,
    TRUE ~ BDL
    ), # close case_when
  BDL = as.factor(BDL)
  ) %>% # close mutate BDL
select(-`ID`, -`month/date`) %>%
  arrange(date, `site number`) %>%
  filter(!is.na(date))

# write_attributes(arsenic)
# write_factors(arsenic)

arsenic_desc <- "arsenic and perchlorate concentrations in canals and reservoirs"

arsenic_DT <- create_dataTable(
  dfname = arsenic,
  description = arsenic_desc)

```

## carbon

```{r carbon, eval=TRUE}

# carbon <- read_csv("data/Carbon_doc_month.csv") %>%
carbon <- read_csv("data/doc_month.csv") %>%
  rename(`cluster` = `cluster name`) %>%
  mutate(
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site number` = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    `sample type` = as.factor(`sample type`),
    date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
    date = as.Date(date)
    ) %>%
  select(-`ID`, -`month`, -Field1) %>%
  arrange(date, `site number`) %>%
  filter(!is.na(date))

# write_attributes(carbon)
# write_factors(carbon)

carbon_desc <- "approximately monthly water carbon data in Phoenix-area canals and reservoirs"

carbon_DT <- create_dataTable(
  dfname = carbon,
  description = carbon_desc)

```

## field_measurements

```{r field_measurements, eval=TRUE}

system("sed -i 's/Secchi Disk, m/Secchi Disk (m)/' data/field_measurements.csv")

field_measurements <- read_csv("data/field_measurements.csv") %>%
  # drop empty cols
  select_if(function(x) { !all(is.na(x)) }) %>%
  rename(
    `cluster` = `cluster name` #,
    #     `Secchi disk (m)` = `Secchi Disk, m`
    ) %>%
  mutate(
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site number` = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    # `sample type` = as.factor(`sample type`),
    date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
    date = as.Date(date)
    ) %>%
  select(-`ID`, -`month`) %>%
  arrange(date, `site number`) %>%
  filter(!is.na(date))

# write_attributes(field_measurements)
# write_factors(field_measurements)

field_measurements_desc <- "water quality parameters as measured in the field in canals and reservoirs"

field_measurements_DT <- create_dataTable(
  dfname = field_measurements,
  description = field_measurements_desc)

```

## microbial

Update 2020-07-06 v3: discovered an error in an earlier version where I changed
character na to flags in the Coliform and Mycobaterium columns. Fixed for
version 3. Note that with this update, there are only flags for Mycobacterium.

Marisa has flags in the Mycobacterium count fields. This information is lost if
converted to numeric. So, I have pulled those text flags out of the count
fields and put them in new flag fields as factors. Note other things here too
like changing some N/A entries to NA, and since I was doing so much
manipulating anyway, I went ahead and made the field names a bit more pleasant.

```{r microbial, eval=TRUE}

microbial <- read_csv("data/Microbial.csv") %>%
  # drop empty cols
  select_if(function(x) { !all(is.na(x)) }) %>%
  rename(
    `site number` = `Site Number`,
    `site location` = `Site Location`,
    `cluster` = `Cluster Name`,
    `site acronym` = `Site Acronym`,
    `date` = `Date`,
    coliform = `Coliform(colonies per 100mL)`,
    mycobacterium = `Mycobacterium(colonies per 100mL)`,
    e_coli = `E coli(colonies per 100mL)`
    ) %>%
  mutate(
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site number` = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    e_coli = case_when(
      grepl("n/a", e_coli, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ e_coli
      ),
    e_coli = as.numeric(e_coli),
    coliform = case_when(
      grepl("n/a", coliform, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ coliform
      ),
    coliform = as.numeric(coliform),
    mycobacterium = case_when(
      grepl("n/a", mycobacterium, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ mycobacterium
      ),
    mycobacterium_flag = case_when(
      grepl("[A-z]+", mycobacterium) ~ str_extract(mycobacterium, "[A-z]+")
      ),
    mycobacterium = as.numeric(mycobacterium),
    mycobacterium_flag = as.factor(mycobacterium_flag),
    date = format(as.POSIXct(date, format = "%m/%d/%Y"), "%Y-%m-%d"),
    date = as.Date(date)
    ) %>%
  select(
    "site number",
    "site location",
    "cluster",
    "site acronym",
    "date",
    "e_coli",
    "coliform",
    "mycobacterium",
    "mycobacterium_flag",
    "Comments"
    ) %>%
  filter(!is.na(date)) %>%
  arrange(date, `site number`)

# write_attributes(microbial)
# write_factors(microbial)

microbial_desc <- "E. coli, Coliform, and Mycobacterium colony counts in canals and reservoirs"

microbial_DT <- create_dataTable(
  dfname = microbial,
  description = microbial_desc)

```

## nutrients

```{r nutrients, eval=TRUE}

system("sed -i 's/NO3-N, mg\\/l/nitrate_nitrogen/' data/nutrients.csv")
system("sed -i 's/NH4-N, ppm/ammonium_nitrogen/' data/nutrients.csv")
system("sed -i 's/DON, ppm/dissolved_organic_nitrogen/' data/nutrients.csv")

# need to force col types owing to big chunks of no data
nutrients <- read_csv(
  file = "data/nutrients.csv",
  col_types = list(
    col_double(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_character(),
    col_double(),
    col_double(),
    col_double(),
    col_double(),
    col_double(),
    col_double(),
    col_double(),
    col_character()
  )
  ) %>%
rename(
  `cluster` = `cluster name`,
  total_nitrogen = `Tot N (mg/L (0<mdl))`,
  total_dissolved_nitrogen = `Diss N (mg/L (0<mdl))`,
  total_phosphorus = `Tot P (ug/L (0<mdl))`,
  total_dissolved_phosphorus = `Diss P (ug/L (0<mdl))` #,
  #   nitrate_nitrogen = `NO3-N, mg/l`,
  #   ammonium_nitrogen = `NH4-N, ppm`,
  #   dissolved_organic_nitrogen = `DON, ppm`,
  ) %>%
mutate(
  cluster = tolower(cluster),
  cluster = as.factor(cluster),
  `site number` = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date = as.Date(date)
  ) %>%
select(-`ID`, -`month`) %>%
arrange(date, `site number`) %>%
filter(!is.na(date))

# write_attributes(nutrients)
# write_factors(nutrients)

nutrients_desc <- "concentration of algal by-products in canals and reservoirs"

nutrients_DT <- create_dataTable(
  dfname = nutrients,
  description = nutrients_desc)

```

## quarterly_lake_sampling

```{r quarterly_lake_sampling, eval=TRUE}

quarterly_lake_sampling <- read_csv("data/Quarterly Lake Sampling.csv") %>%
  rename(
    `cluster` = `Cluster Name`,
    `site number` = `Site Name`,
    `site location` = `Site Location`,
    `site acronym` = `Site Acronym`,
    `date` = `Date`,
    `MIB (ng/L)` = `Mib(ng/L)`,
    `geosmin (ng/L)` = `Geosmin(ng/L)`,
    `UVA (cm-1)` = `UVA(cm-1)`,
    `Suva(L/mg-m)` = `Suva(L/mg-m)`,
    `Conductance (us/cm)` = `Conductance(us/cm)`
    ) %>%
mutate(
  cluster = tolower(cluster),
  cluster = as.factor(cluster),
  `site number` = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date = as.Date(date)
  ) %>%
select(-`ID`) %>%
arrange(date, `site number`) %>%
filter(!is.na(date))

# write_attributes(quarterly_lake_sampling)
# write_factors(quarterly_lake_sampling)

quarterly_lake_sampling_desc <- "concentration of nutrients and algal by-products, and other water quality parameters measured in central-Arizona area lakes"

quarterly_lake_sampling_DT <- create_dataTable(
  dfname = quarterly_lake_sampling,
  description = quarterly_lake_sampling_desc)

```

### quarterly_metals

```{r quarterly_metals, eval=TRUE}

quarterly_metals <- read_csv("data/Quarterly Metals.csv") %>%
  # drop empty cols
  select_if(function(x) { !all(is.na(x)) }) %>%
  rename(
    `cluster` = `Cluster Name`,
    `site number` = `Site Name`,
    `site location` = `Site Location`,
    `site acronym` = `Site Acronym`,
    `date` = `Date`,
    `units` = `Units`
    ) %>%
  mutate(
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site number` = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    date = format(as.POSIXct(`date`, format = "%m/%d/%Y"), "%Y-%m-%d"),
    date = as.Date(date)
    ) %>%
  select(-`ID`, -units) %>%
  arrange(date, `site number`) %>%
  filter(!is.na(date))

# write_attributes(quarterly_metals)
# write_factors(quarterly_metals)

quarterly_metals_desc <- "concentration of dissolved metals measured in central-Arizona area lakes and canals"

quarterly_metals_DT <- create_dataTable(
  dfname = quarterly_metals,
  description = quarterly_metals_desc)

```

## sampling_locations

```{r sampling_locations, eval=TRUE}

sampling_locations <- read_csv("data/gpscoord.csv") %>%
  rename(
    `cluster` = `cluster name`,
    `latitude` = `laditude`
    ) %>%
mutate(
  cluster = tolower(cluster),
  cluster = as.factor(cluster),
  `site number` = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date = as.Date(date),
  latitude = case_when(
    `site number` %in% c("R9A", "R9B") ~ "N33o34.053",
    TRUE ~ latitude
  )
  ) %>%
select(-`ID`) %>%
arrange(date, `site number`) %>%
filter(!is.na(date))

sampling_locations$longitude = gsub("W", "", sampling_locations$longitude)
sampling_locations$longitude = gsub("o", " ", sampling_locations$longitude)
sampling_locations$latitude = gsub("N", "", sampling_locations$latitude)
sampling_locations$latitude = gsub("o", " ", sampling_locations$latitude)

sampling_locations$longitude = measurements::conv_unit(sampling_locations$longitude, from = "deg_dec_min", to = "dec_deg")
sampling_locations$latitude = measurements::conv_unit(sampling_locations$latitude, from = "deg_dec_min", to = "dec_deg")

sampling_locations$longitude <- as.numeric(as.character(sampling_locations$longitude)) * -1
sampling_locations$latitude <- as.numeric(as.character(sampling_locations$latitude))

# write_attributes(sampling_locations)
# write_factors(sampling_locations)

sampling_locations_desc <- "latitude, longitude, and elevation of select canal, lake, and river water-quality sampling locations"

sampling_locations_DT <- create_dataTable(
  dfname = sampling_locations,
  description = sampling_locations_desc)

```


```{r title, eval=FALSE}

title <- "Regional drinking water quality monitoring program: long-term monitoring of water quality in select canals, reservoirs, and treatment plants of the greater Phoenix, Arizona metropolitan area drinking water system, ongoing since 1998"
```

## people

```{r people}

# see gioseml for examples of creating people resources from scratch

source("~/Documents/localSettings/mysql_prod.R")
mysql_prod <- mysql_prod_connect()

peter <- create_role(firstName = "peter", lastName = "fox", roleType = "creator")
morteza <- create_role(firstName = "m", lastName = "abbaszadegan", roleType = "creator")

creators <- list(peter, morteza)

marisa <- create_role(firstName = "m", lastName = "masles", roleType = "metadata")
metadataProvider <- list(marisa)

paul <- create_role(firstName = "p", lastName = "westerhoff", roleType = "associated")
milt <- create_role(firstName = "m", lastName = "sommerfeld", roleType = "associated")

associatedParty <- list(paul, milt)

```

# keywords

```{r keywords}

# CAP IRTs for reference (be sure to include these as appropriate):
# https://sustainability.asu.edu/caplter/research/

write_keywords()
```

# methods

Methods are automatically read from a `methods.md` file in the project
directory. If more elaborate methods are required, e.g., to incorporate
provenance, use the enhancedMethods approach outlined in the capeml package.


```{r coverages}

allDates <- rbind(
  algae[, "date"],
  nutrients[, "date"],
  quarterly_lake_sampling[, "date"],
  quarterly_metals[, "date"],
  algal_byproducts[, "date"],
  arsenic[, "date"],
  carbon[, "date"],
  field_measurements[, "date"],
  microbial[, "date"]
)

begindate <- as.character(min(allDates$date))
enddate <- as.character(max(allDates$date))

geographicDescription <- "canals, water treatment plants, and reservoirs in the greater phoenix metropolitan area"

coverage <- set_coverage(
  begin = begindate,
  end = enddate,
  geographicDescription = geographicDescription,
  west = -111.1250, east = -111.1235,
  north = +33.4900, south = +33.2917)

```


# dataset

Optionally, provide: scope, abstract, methods, keywords, publication date.
Projects scopes include lter (default), urex, and som.

```{r construct-dataset}

dataset <- create_dataset()
```

# add dataTable

```{r dataSet$dataTable}

# add dataTables if relevant

print(ls(pattern = "_DT"))

if (length(ls(pattern = "_DT")) > 0) {
  
  listOfDataTables <- lapply(ls(pattern = "_DT"), function(DT) { get(DT) } )
  
  dataset$dataTable  <- listOfDataTables  
  
}

# or add manually
# dataset$dataTable <- list(algae_DT)

```


# customUnits

```{r custom-units, eval=TRUE}

custom_units <- rbind(
  data.frame(id = "microsiemenPerCentimeter",
             unitType = "conductance",
             parentSI = "siemen",
             multiplierToSI = 0.000001,
             description = "electric conductance of lake water in the units of microsiemenPerCentimeter"),
  data.frame(id = "perCentimeter",
             unitType = "unknown",
             parentSI = "unknown",
             multiplierToSI = "unknown",
             description = "absorbance per centimeter of path length at 254 nm"),
  data.frame(id = "literPerMilligramMeter",
             unitType = "unknown",
             parentSI = "unknown",
             multiplierToSI = "unknown",
             description = "the UV absorbance at 254 nanometers measured in inverse meters divided by the DOC concentration measured in milligrams per liter"),
  data.frame(id = "nanogramsPerLiter",
             unitType = "amountOfSubstanceConcentration",
             parentSI = "kilogram/cubic meter",
             multiplierToSI = 0.000001,
             description = "nanograms of material per liter of solute"),
  data.frame(id = "coloniesPer100milliliter",
             unitType = "unknown",
             parentSI = "unknown",
             multiplierToSI = "unknown",
             description = "number of bacterial colonies formed per 100 millileters of water"))

unitList <- set_unitList(custom_units,
                         as_metadata = TRUE)

```


# eml

```{r construct_eml, eval=TRUE}

eml <- create_eml()
```

```{r package-details, eval=TRUE}

# retrieve package details from config.yaml
if (!file.exists("config.yaml")) {
  stop("config.yaml not found")
}
packageIdent <- yaml::yaml.load_file("config.yaml")$packageIdent
packageNum <- yaml::yaml.load_file("config.yaml")$packageNum
```

```{r write_eml, eval=TRUE}

# write the eml to file
write_eml(eml, paste0(packageIdent, ".xml"))
```

# file placement

```{r preview_data_file_to_upload}

# preview data set files that will be uploaded to S3
list.files(pattern = paste0(packageNum, "_"))
```

Move data and final xml files to respective ASU locations.

```{r S3_helper_functions}

# functions and setting for uploading to S3
library(aws.s3)
source('~/Documents/localSettings/aws.s3')
```

```{r upload_data_S3}

# upload files to S3
lapply(list.files(pattern = paste0(packageNum, "_")), data_to_amz)
```

```{r clean_up}

# remove data files
dataFilesToRemove <- dir(pattern = paste0(packageNum, "_"))
file.remove(dataFilesToRemove)

# EML to S3
if(length(list.files(pattern = "*.xml")) == 1) {
  eml_to_amz(list.files(pattern = "*.xml")) } else {
    print("more than one xml file found")
  }

# EML to cap-data-eml and remove file from project
tryCatch({
  
  if(length(list.files(pattern = "*.xml")) == 1) {
    file.copy(list.files(pattern = "*.xml"), "/home/srearl/localRepos/cap-metadata/cap-data-eml/")
    file.remove(list.files(pattern = "*.xml")) } else {
      print("more than one xml file found")
    }
},
warning = function(warn) {
  print(paste("WARNING: ", warn))
},
error = function(err) {
  print(paste("ERROR: ", err))
  
}) # close try catch
```
