---
title: "remlTemplate"
author: "SRE"
date: Sys.Date()
output: html_document
editor_options:
  chunk_output_type: console
---

# README

see project README for extracting data from Access database.


# project details

see config.yaml

# data entities

## algae

```{r algae, eval=TRUE, error=TRUE}

algae <- readr::read_csv("data/Conductivity.csv") |>
  dplyr::rename(cluster = `cluster name`) |>
  dplyr::mutate(
    `site number`  = as.factor(`site number`),
    cluster        = tolower(cluster),
    cluster        = as.factor(cluster),
    `site acronym` = as.factor(`site acronym`),
    `sample type`  = as.factor(`sample type`),
    date           = format(as.POSIXct(date, format = "%m/%d/%y %H:%M:%S"), "%Y-%m-%d"),
    date           = as.Date(date)
  ) |>
  dplyr::select(-ID, -month) |>
  dplyr::arrange(date, `site number`) |>
  dplyr::filter(!is.na(date))

# try({
#   capeml::write_attributes(algae, overwrite = FALSE)
#   capeml::write_factors(algae, overwrite = FALSE)
# })

capeml::update_attributes(algae)

# algae_desc <- "algal characteristics (chlorophyll concentration, cell counts) and specific conductance in canals and reservoirs"

# algae_DT <- capeml::create_dataTable(
#   dfname         = algae,
#   description    = algae_desc,
#   dateRangeField = "date",
#   overwrite      = TRUE
# )

```


## algal_byproducts

```{r algal_byproducts, eval=TRUE}

algal_byproducts <- readr::read_csv(
  file = "data/mib and geosmin.csv",
  guess_max = Inf
  ) |>
  dplyr::rename(
    `cluster`                 = `cluster name`,
    `geosmin (ng/L) ASU`      = `Geosmin  (ng/L) ASU`,
    `beta-cyclocitral (ng/L)` = `Beta-cyclocitral (ng/L)`,
    `IPMP recovery (%)`       = `IPMP Recovery (%)`,
    `geosmin (ng/L) Phoenix`  = `Geosmin  (ng/L) Phoenix`
    ) |>
  dplyr::mutate(
    cluster        = tolower(cluster),
    cluster        = as.factor(cluster),
    `site number`  = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
    date           = as.Date(date),
    comments       = as.character(comments)
    ) |>
  dplyr::select(-`ID`, -`month`) |>
  dplyr::arrange(date, `site number`) |>
  dplyr::filter(!is.na(date))

capeml::update_attributes(algal_byproducts)

# try({
#   capeml::write_attributes(algal_byproducts, overwrite = FALSE)
#   capeml::write_factors(algal_byproducts, overwrite = FALSE)
# })

# algal_byproducts_desc <- "concentration of algal by-products in canals and reservoirs"

# algal_byproducts_DT <- capeml::create_dataTable(
#   dfname         = algal_byproducts,
#   description    = algal_byproducts_desc,
#   dateRangeField = "date"
# )

```

## arsenic

```{r arsenic, eval=TRUE}

# complicated import and mutate actions to accommodate text (<2.0) in the
# arsenic concentration column

arsenic <- readr::read_csv(
  file      = "data/Arsenic.csv",
  col_types = list(
    readr::col_double(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_double()
  )
  ) |>
dplyr::rename(
  `cluster`            = `Cluster`,
  `site number`        = `Site Number`,
  `site location`      = `Site location`,
  `site acronym`       = `Site Acronym`,
  `arsenic (ug/L)`     = `Arsenic (ug/L)`,
  `perchlorate (ug/L)` = `Perchlorate (ug/L)`
  ) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date           = format(as.POSIXct(`month/date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date           = as.Date(date)
  ) |>
dplyr::mutate(
  BDL = dplyr::case_when(
    grepl("<2.0", `arsenic (ug/L)`, ignore.case = T) ~ 1
  )
  ) |> # close dplyr::mutate BDL
dplyr::mutate(
  `arsenic (ug/L)` = as.numeric(`arsenic (ug/L)`),
  BDL = dplyr::case_when(
    `arsenic (ug/L)` < 2 ~ 1,
    TRUE ~ BDL
    ), # close dplyr::case_when
  BDL = as.factor(BDL)
  ) |> # close dplyr::mutate BDL
dplyr::select(-`ID`, -`month/date`) |>
dplyr::arrange(date, `site number`) |>
dplyr::filter(!is.na(date))

capeml::update_attributes(arsenic)

# try({
#   capeml::write_attributes(arsenic, overwrite = FALSE)
#   capeml::write_factors(arsenic, overwrite = FALSE)
# })

# arsenic_desc <- "arsenic and perchlorate concentrations in canals and reservoirs"

# arsenic_DT <- capeml::create_dataTable(
#   dfname         = arsenic,
#   description    = arsenic_desc,
#   dateRangeField = "date"
#   )

```

## carbon

```{r carbon, eval=TRUE}

# carbon <- readr::read_csv("data/Carbon_doc_month.csv") |>
carbon <- readr::read_csv(
  file = "data/doc_month.csv",
  col_types = readr::cols(
    `docm comments` = "c"
  )
  ) |>
dplyr::rename(`cluster` = `cluster name`) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  `sample type`  = as.factor(`sample type`),
  date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date           = as.Date(date)
  ) |>
dplyr::select(-`ID`, -`month`, -Field1) |>
dplyr::arrange(date, `site number`) |>
dplyr::filter(!is.na(date))

capeml::update_attributes(carbon)

# try({
#   capeml::write_attributes(carbon, overwrite = FALSE)
#   capeml::write_factors(carbon, overwrite = FALSE)
# })

# carbon_desc <- "approximately monthly water carbon data in Phoenix-area canals and reservoirs"

# carbon_DT <- capeml::create_dataTable(
#   dfname         = carbon,
#   description    = carbon_desc,
#   dateRangeField = "date"
# )

```

## field_measurements

```{r field_measurements, eval=TRUE}

system("sed -i 's/Secchi Disk, m/Secchi Disk (m)/' data/field_measurements.csv")

field_measurements <- readr::read_csv("data/field_measurements.csv") |>
# drop empty cols
dplyr::select_if(function(x) { !all(is.na(x)) }) |>
dplyr::rename(
  `cluster` = `cluster name`
  ) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  # `sample type` = as.factor(`sample type`),
  date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date           = as.Date(date)
  ) |>
dplyr::select(-`ID`, -`month`) |>
dplyr::arrange(date, `site number`) |>
dplyr::filter(!is.na(date))

capeml::update_attributes(field_measurements)

# try({
#   capeml::write_attributes(field_measurements, overwrite = FALSE)
#   capeml::write_factors(field_measurements, overwrite = FALSE)
# })

# field_measurements_desc <- "water quality parameters as measured in the field in canals and reservoirs"

# field_measurements_DT <- capeml::create_dataTable(
#   dfname         = field_measurements,
#   description    = field_measurements_desc,
#   dateRangeField = "date"
# )

```

## microbial

Update 2020-07-06 v3: discovered an error in an earlier version where I changed
character na to flags in the Coliform and Mycobaterium columns. Fixed for
version 3. Note that with this update, there are only flags for Mycobacterium.

Marisa has flags in the Mycobacterium count fields. This information is lost if
converted to numeric. So, I have pulled those text flags out of the count
fields and put them in new flag fields as factors. Note other things here too
like changing some N/A entries to NA, and since I was doing so much
manipulating anyway, I went ahead and made the field names a bit more pleasant.

```{r microbial, eval=TRUE}

microbial <- readr::read_csv("data/Microbial.csv") |>
  # drop empty cols
  dplyr::select_if(function(x) { !all(is.na(x)) }) |>
  dplyr::rename(
    `site number`   = `Site Number`,
    `site location` = `Site Location`,
    `cluster`       = `Cluster Name`,
    `site acronym`  = `Site Acronym`,
    `date`          = `Date`,
    coliform        = `Coliform(colonies per 100mL)`,
    mycobacterium   = `Mycobacterium(colonies per 100mL)`,
    e_coli          = `E coli(colonies per 100mL)`
    ) |>
  dplyr::mutate(
    cluster = tolower(cluster),
    cluster = as.factor(cluster),
    `site number` = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    e_coli = dplyr::case_when(
      grepl("n/a", e_coli, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ e_coli
      ),
    e_coli = as.numeric(e_coli),
    coliform = dplyr::case_when(
      grepl("n/a", coliform, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ coliform
      ),
    coliform = as.numeric(coliform),
    mycobacterium = dplyr::case_when(
      grepl("n/a", mycobacterium, ignore.case = TRUE) ~ NA_character_,
      TRUE ~ mycobacterium
      ),
    mycobacterium_flag = dplyr::case_when(
      grepl("[A-z]+", mycobacterium) ~ stringr::str_extract(mycobacterium, "[A-z]+")
      ),
    mycobacterium = as.numeric(mycobacterium),
    mycobacterium_flag = as.factor(mycobacterium_flag),
    date = format(as.POSIXct(date, format = "%m/%d/%Y"), "%Y-%m-%d"),
    date = as.Date(date)
    ) |>
  dplyr::select(
    "site number",
    "site location",
    "cluster",
    "site acronym",
    "date",
    "e_coli",
    "coliform",
    "mycobacterium",
    "mycobacterium_flag",
    "Comments"
    ) |>
  dplyr::filter(!is.na(date)) |>
  dplyr::arrange(date, `site number`)

capeml::update_attributes(microbial)

# try({
#   capeml::write_attributes(microbial, overwrite = FALSE)
#   capeml::write_factors(microbial, overwrite = FALSE)
# })

# microbial_desc <- "E. coli, Coliform, and Mycobacterium colony counts in canals and reservoirs"

# microbial_DT <- capeml::create_dataTable(
#   dfname         = microbial,
#   description    = microbial_desc,
#   dateRangeField = "date"
# )

```

## nutrients

```{r nutrients, eval=TRUE}

system("sed -i 's/NO3-N, mg\\/l/nitrate_nitrogen/' data/nutrients.csv")
system("sed -i 's/NH4-N, ppm/ammonium_nitrogen/' data/nutrients.csv")
system("sed -i 's/DON, ppm/dissolved_organic_nitrogen/' data/nutrients.csv")

# need to force col types owing to big chunks of no data
nutrients <- readr::read_csv(
  file = "data/nutrients.csv",
  col_types = list(
    readr::col_double(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_character(),
    readr::col_double(),
    readr::col_double(),
    readr::col_double(),
    readr::col_double(),
    readr::col_double(),
    readr::col_double(),
    readr::col_double(),
    readr::col_character()
  )
  ) |>
dplyr::rename(
  `cluster`                  = `cluster name`,
  total_nitrogen             = `Tot N (mg/L (0<mdl))`,
  total_dissolved_nitrogen   = `Diss N (mg/L (0<mdl))`,
  total_phosphorus           = `Tot P (ug/L (0<mdl))`,
  total_dissolved_phosphorus = `Diss P (ug/L (0<mdl))` #,
  #   nitrate_nitrogen = `NO3-N, mg/l`,
  #   ammonium_nitrogen = `NH4-N, ppm`,
  #   dissolved_organic_nitrogen = `DON, ppm`,
  ) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date           = as.Date(date)
  ) |>
dplyr::select(-`ID`, -`month`) |>
dplyr::arrange(date, `site number`) |>
dplyr::filter(!is.na(date))

capeml::update_attributes(nutrients)

# try({
#   capeml::write_attributes(nutrients, overwrite = FALSE)
#   capeml::write_factors(nutrients, overwrite = FALSE)
# })

# nutrients_desc <- "concentration of algal by-products in canals and reservoirs"

# nutrients_DT <- capeml::create_dataTable(
#   dfname         = nutrients,
#   description    = nutrients_desc,
#   dateRangeField = "date"
# )

```

## quarterly_lake_sampling

```{r quarterly_lake_sampling, eval=TRUE}

quarterly_lake_sampling <- readr::read_csv("data/Quarterly Lake Sampling.csv") |>
  dplyr::rename(
    `cluster`             = `Cluster Name`,
    `site number`         = `Site Name`,
    `site location`       = `Site Location`,
    `site acronym`        = `Site Acronym`,
    `date`                = `Date`,
    `MIB (ng/L)`          = `Mib(ng/L)`,
    `geosmin (ng/L)`      = `Geosmin(ng/L)`,
    `UVA (cm-1)`          = `UVA(cm-1)`,
    `Suva(L/mg-m)`        = `Suva(L/mg-m)`,
    `Conductance (us/cm)` = `Conductance(us/cm)`
    ) |>
  dplyr::mutate(
    cluster        = tolower(cluster),
    cluster        = as.factor(cluster),
    `site number`  = as.factor(`site number`),
    `site acronym` = as.factor(`site acronym`),
    date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
    date           = as.Date(date)
    ) |>
  dplyr::select(-`ID`) |>
  dplyr::arrange(date, `site number`) |>
  dplyr::filter(!is.na(date))

capeml::update_attributes(quarterly_lake_sampling)

# try({
#   capeml::write_attributes(quarterly_lake_sampling, overwrite = FALSE)
#   capeml::write_factors(quarterly_lake_sampling, overwrite = FALSE)
# })

# quarterly_lake_sampling_desc <- "concentration of nutrients and algal by-products, and other water quality parameters measured in central-Arizona area lakes"

# quarterly_lake_sampling_DT <- capeml::create_dataTable(
#   dfname         = quarterly_lake_sampling,
#   description    = quarterly_lake_sampling_desc,
#   dateRangeField = "date",
#   overwrite      = TRUE
# )

```

## quarterly_metals

```{r quarterly_metals, eval=TRUE}

quarterly_metals <- readr::read_csv("data/Quarterly Metals.csv") |>
# drop empty cols
dplyr::select_if(function(x) { !all(is.na(x)) }) |>
dplyr::rename(
  `cluster`       = `Cluster Name`,
  `site number`   = `Site Name`,
  `site location` = `Site Location`,
  `site acronym`  = `Site Acronym`,
  `date`          = `Date`,
  `units`         = `Units`
  ) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date           = format(as.POSIXct(`date`, format = "%m/%d/%Y"), "%Y-%m-%d"),
  date           = as.Date(date)
  ) |>
dplyr::select(-`ID`, -units) |>
dplyr::arrange(date, `site number`) |>
dplyr::filter(!is.na(date))

capeml::update_attributes(quarterly_metals)

# try({
#   capeml::write_attributes(quarterly_metals, overwrite = FALSE)
#   capeml::write_factors(quarterly_metals, overwrite = FALSE)
# })

# quarterly_metals_desc <- "concentration of dissolved metals measured in central-Arizona area lakes and canals"

# quarterly_metals_DT <- capeml::create_dataTable(
#   dfname         = quarterly_metals,
#   description    = quarterly_metals_desc,
#   dateRangeField = "date"
# )

```

## sampling_locations

```{r sampling_locations, eval=TRUE}

sampling_locations <- readr::read_csv("data/gpscoord.csv") |>
dplyr::rename(
  `cluster`  = `cluster name`,
  `latitude` = `laditude`
  ) |>
dplyr::mutate(
  cluster        = tolower(cluster),
  cluster        = as.factor(cluster),
  `site number`  = as.factor(`site number`),
  `site acronym` = as.factor(`site acronym`),
  date           = format(as.POSIXct(`date`, format = "%m/%d/%y"), "%Y-%m-%d"),
  date           = as.Date(date),
  latitude       = dplyr::case_when(
    `site number` %in% c("R9A", "R9B") ~ "N33o34.053",
    TRUE ~ latitude
  )
  ) |>
dplyr::select(-`ID`) |>
dplyr::arrange(date, `site number`) # |>
# dplyr::filter(!is.na(date))


sampling_locations$longitude = gsub("W", "", sampling_locations$longitude)
sampling_locations$longitude = gsub("o", " ", sampling_locations$longitude)
sampling_locations$latitude  = gsub("N", "", sampling_locations$latitude)
sampling_locations$latitude  = gsub("o", " ", sampling_locations$latitude)

sampling_locations$longitude = measurements::conv_unit(sampling_locations$longitude, from = "deg_dec_min", to = "dec_deg")
sampling_locations$latitude  = measurements::conv_unit(sampling_locations$latitude, from = "deg_dec_min", to = "dec_deg")

sampling_locations$longitude <- as.numeric(as.character(sampling_locations$longitude)) * -1
sampling_locations$latitude  <- as.numeric(as.character(sampling_locations$latitude))

capeml::update_attributes(sampling_locations)

# try({
#   capeml::write_attributes(sampling_locations, overwrite = FALSE)
#   capeml::write_factors(sampling_locations, overwrite = FALSE)
# })

# sampling_locations_desc <- "latitude, longitude, and elevation of select canal, lake, and river water-quality sampling locations"

# sampling_locations_DT <- capeml::create_dataTable(
#   dfname      = sampling_locations,
#   description = sampling_locations_desc
# )

```


# people

```{r people}

ds <- "~/Dropbox/floating/cap_authors.csv"

# creators

peter <- gioseml::create_role(
  lastName   = "fox",
  dataSource = ds,
  roleType   = "creator"
)

morteza <- gioseml::create_role(
  lastName   = "abbaszadegan",
  dataSource = ds,
  roleType   = "creator"
)

creators <- list(peter, morteza)

# metadata provider

marisa <- gioseml::create_role(
  lastName   = "masles",
  dataSource = ds,
  roleType   = "meta"
)

metadataProvider <- list(marisa)

# associates

paul <- gioseml::create_role(
  lastName   = "westerhoff",
  dataSource = ds,
  roleType   = "assoc"
)


milt <- gioseml::create_role(
  lastName   = "sommerfeld",
  dataSource = ds,
  roleType   = "assoc"
)

associatedParty <- list(paul, milt)

```

# keywords

```{r keywords}

# CAP IRTs for reference (be sure to include these as appropriate):
# https://sustainability.asu.edu/caplter/research/

write_keywords()
```

# methods

Methods are automatically read from a `methods.md` file in the project
directory. If more elaborate methods are required, e.g., to incorporate
provenance, use the enhancedMethods approach outlined in the capeml package.


# coverage

```{r coverages}

# sampling_locations |>
# dplyr::filter(!is.na(longitude)) |>
# sf::st_as_sf(
#   coords = c("longitude", "latitude"),
#   crs    = 4326
# ) |>
# mapview::mapview()

allDates <- rbind(
  algae[, "date"],
  nutrients[, "date"],
  quarterly_lake_sampling[, "date"],
  quarterly_metals[, "date"],
  algal_byproducts[, "date"],
  arsenic[, "date"],
  carbon[, "date"],
  field_measurements[, "date"],
  microbial[, "date"]
)

begindate <- as.character(min(allDates$date))
enddate   <- as.character(max(allDates$date))

bbox <- sampling_locations |>
dplyr::filter(
  !is.na(longitude)
) |>
sf::st_as_sf(
  coords = c("longitude", "latitude"),
  crs    = 4326
) |>
sf::st_bbox(map)

coverage <- EML::set_coverage(
  begin                 = begindate,
  end                   = enddate,
  geographicDescription = yaml::yaml.load_file("config.yaml")$geographic_description,
  west                  = bbox[["xmin"]],
  east                  = bbox[["xmax"]],
  north                 = bbox[["ymax"]],
  south                 = bbox[["ymin"]]
)

```


# dataset

```{r construct-dataset}

dataset <- capeml::create_dataset()
```


# customUnits

```{r custom-units, eval=TRUE}

custom_units <- rbind(
  data.frame(
    id             = "microsiemensPerCentimeter",
    unitType       = "conductance",
    parentSI       = "siemen",
    multiplierToSI = 0.000001,
    description    = "electric conductance of lake water in the units of microsiemensPerCentimeter"
    ),
  data.frame(
    id             = "perCentimeter",
    unitType       = "unknown",
    parentSI       = "unknown",
    multiplierToSI = "unknown",
    description    = "absorbance per centimeter of path length at 254 nm"
    ),
  data.frame(
    id             = "literPerMilligramMeter",
    unitType       = "unknown",
    parentSI       = "unknown",
    multiplierToSI = "unknown",
    description    = "the UV absorbance at 254 nanometers measured in inverse meters divided by the DOC concentration measured in milligrams per liter"
    ),
  data.frame(
    id             = "nanogramsPerLiter",
    unitType       = "amountOfSubstanceConcentration",
    parentSI       = "kilogram/cubic meter",
    multiplierToSI = 0.000001,
    description    = "nanograms of material per liter of solute"
    ),
  data.frame(
    id             = "coloniesPer100milliliter",
    unitType       = "unknown",
    parentSI       = "unknown",
    multiplierToSI = "unknown",
    description    = "number of bacterial colonies formed per 100 millileters of water"
  )
)

unitList <- EML::set_unitList(
  custom_units,
  as_metadata = TRUE
)

```


# eml

```{r construct_eml, eval=TRUE}

eml <- capeml::create_eml()
```

```{r validate_eml, eval=TRUE}

EML::eml_validate(eml)
```

```{r eml_to_file, eval=TRUE}

# write the eml to file
capeml::write_cap_eml()
```


# file placement: data files

## read package details

```{r package-details, eval=TRUE}

# retrieve package details from config.yaml
if (!file.exists("config.yaml")) {
  stop("config.yaml not found")
}
package_configs <- capeml::read_package_configuration()
identifier      <- package_configs$identifier
scope           <- package_configs$scope

version <- capeml::get_next_version(
  provided_scope      = scope,
  provided_identifier = identifier
)
```

## preview data files upload

```{r preview-data-file-to-upload}

list.files(pattern = paste0(identifier, "_"))
```

## source AWS S3 settings

```{r S3-helper-functions}

# library(aws.s3)
source("~/Documents/localSettings/aws.s3")
```

## upload data files to S3

```{r upload-data-S3}

lapply(list.files(pattern = paste0(identifier, "_")), capeml::data_to_amz)
```


# EDI

## EDI: login

```{r edi-login, eval=TRUE, echo=TRUE, message=TRUE}

EDIutils::login(
  userId   = keyring::key_get("edi_user", keyring = "edi"),
  userPass = keyring::key_get("edi_pass", keyring = "edi")
)

```

## EDI: evaluate

```{r edi-evaluate, eval=TRUE, echo=TRUE, message=TRUE}

evaluation <- EDIutils::evaluate_data_package(
  eml         = paste(scope, identifier, version, "xml", sep = "."),
  useChecksum = FALSE,
  env         = "staging"
)

Sys.sleep(8)

eval_status <- EDIutils::check_status_evaluate(
  transaction = evaluation,
  env         = "staging"
)

if (eval_status) {

  # evaluation summary

  EDIutils::read_evaluate_report_summary(
    transaction = evaluation,
    env         = "staging"
  )

}

# evaluation detailed

EDIutils::read_evaluate_report(
  transaction = evaluation,
  env         = "staging"
)

```

## EDI: update

```{r edi-update, eval=TRUE, echo=TRUE, message=TRUE}

EDIutils::update_data_package(
  eml         = paste(scope, identifier, version, "xml", sep = "."),
  useChecksum = TRUE,
  env         = "staging"
)

```

## EDI: logout

```{r edi-logout, eval=TRUE, echo=TRUE, message=TRUE}

EDIutils::logout()

```


# file placement: data files

## read package details

```{r package-details, eval=TRUE}

# retrieve package details from config.yaml
if (!file.exists("config.yaml")) {
  stop("config.yaml not found")
}
package_configs <- capeml::read_package_configuration()
identifier      <- package_configs$identifier
scope           <- package_configs$scope

version <- capeml::get_next_version(
  provided_scope      = scope,
  provided_identifier = identifier
)
```

## preview data files upload

```{r preview-data-file-to-upload}

list.files(pattern = paste0(identifier, "_"))
```

## source AWS S3 settings

```{r S3-helper-functions}

# library(aws.s3)
source("~/Documents/localSettings/aws.s3")
```

## upload data files to S3

```{r upload-data-S3}

lapply(list.files(pattern = paste0(identifier, "_")), capeml::data_to_amz)
```


# post processing

remove data files (if desired)

```{r delete-data-files}

dataFilesToRemove <- dir(pattern = paste0(identifier, "_"))
file.remove(dataFilesToRemove)

```

XML/EML file to Amazon and cap-metadata

```{r delete-data-files}

capeml::eml_to_amz(list.files(pattern = "knb.+xml"))

file.copy(list.files(pattern = "knb.+xml"), "/home/srearl/localRepos/cap-metadata/cap-data-eml/")

file.remove(list.files(pattern = "knb.+xml"))
```
